---
title: "Ryan Tillis - Getting and Cleaning Data - Data Science - Quiz 1 - Coursera"
author: <a href="http://www.ryantillis.com"> Ryan Tillis </a>
date: "July 4, 2016"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Getting and Cleaning Data Quiz 1

This is Quiz 1 from the Getting and Cleaning Data course within the Data Science Specialization on Coursera.

###Questions
<hr>
<font size="+2">1.  </font> The American Community Survey distributes downloadable data about United States communities. Download the 2006 microdata survey about housing for the state of Idaho using download.file() from here:

<https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Fss06hid.csv>

and load the data into R. The code book, describing the variable names is here:

<https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FPUMSDataDict06.pdf>

How many properties are worth $1,000,000 or more?

<hr>

<font size="+1">
<b>

* 53

</b>
</font>

<hr>

```{r Question 1}
download.file("https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Fss06hid.csv", destfile = "quiz1data.csv")
data <- read.csv("quiz1data.csv")
nrow(data[which(data$VAL == 24),])
```

<hr>

<font size="+2">2.  </font> Use the data you loaded from Question 1. Consider the variable FES in the code book. Which of the "tidy data" principles does this variable violate?

<hr>

<font size="+1">
<b>

* Tidy data has one variable per column.

</b>
</font>

<hr>

#####Explanation:

FES        1
    Family type and employment status
b .N/A (GQ/vacant/not a family)
1 .Married-couple family: Husband and wife in LF
2 .Married-couple family: Husband in labor force, wife
             .not in LF
           3 .Married-couple family: Husband not in LF,
.wife in LF
4 .Married-couple family: Neither husband nor wife in
.LF
5 .Other family: Male householder, no wife present, in
.LF
6 .Other family: Male householder, no wife present,
.not in LF
7 .Other family: Female householder, no husband
             .present, in LF
8 .Other family: Female householder, no husband
             .present, not in LF

<hr>

<font size="+2">3.  </font> Download the Excel spreadsheet on Natural Gas Aquisition Program here:

<https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FDATA.gov_NGAP.xlsx>

Read rows 18-23 and columns 7-15 into R and assign the result to a variable called:

```{r dat}
dat
What is the value of:
```

```{r dat2}
sum(dat$Zip*dat$Ext,na.rm=T)
```
(original data source: <http://catalog.data.gov/dataset/natural-gas-acquisition-program>)


<hr>

<font size="+1">
<b>

* 53

</b>
</font>

<hr>

#####Explanation:

Different strokes

<hr>
```{r Question 3}
require(xlsx)
download.file("https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FDATA.gov_NGAP.xlsx", destfile = "quiz1data2.xlsx")
dat <- read.xlsx("quiz1data2.xlsx", sheetIndex = 1, colIndex = colIndex, rowIndex = rowIndex)
```

<hr>

<font size="+2">4.  </font> Continuing with the 'mtcars' dataset from the previous Question, what is the absolute difference between the average horsepower of 4-cylinder cars and the average horsepower of 8-cylinder cars?

(Please round your final answer to the nearest whole number. Only enter the numeric result and nothing else.)

<hr>

<font size="+1">
<b>

* 53

</b>
</font>

<hr>

#####Explanation:

Using the built in looping tapply function to aggregate and then round/abs.

Self-explanatory
```{r Question 4}
new <- tapply(mtcars$hp, mtcars$cyl, mean)
round(abs(new[3]-new[1]))
```

<hr>

<font size="+2">5.  </font> If you run

```{r q5a}
debug(ls)
```

What happens when you next call the 'ls' function?

<hr>

<font size="+1">
<b>

* 53

</b>
</font>

<hr>

#####Explanation:

Debug walks through each block of code to identify errors and bugs.

```{r Question 5}

```

<hr>

Check out my website at: <http://www.ryantillis.com/>

<hr>
